---
title       : caratPrice App
subtitle    : Documentation
author      : Shane B. Bimeda Feb. 17, 2019 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## caratPrice App

The application takes in the **carat value** supplied by the user and uses it as an input in a linear model based on the **diamonds** dataset from the **ggplot2 package**.

The output is the specific value of the **price** as predicted by the model and a plot of the model itself.

--- 

## Dataset used: **Diamonds**

The dataset contains the prices and other attributes of almost 54,000 diamonds. It is composed of 53940 rows and 10 variables that are as follows:

- price
- carat
- cut
- color
- clarity
- length (x, y, z)
- depth
- table

---

## Building the linear model

```{r, comment= FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(ggplot2)

```

```{r, comment= FALSE, echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE}


model1 <- lm(price ~ carat, data = diamonds)

```

The model makes use of a simple linear regression wherein the **y** variable is the **price of the diamond** and the **x** variable is the **carat** of the diamond.

---

## Plot of the Model Used (Residuals vs Fitted)

```{r, comment= FALSE, echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE}

plot(model1)

```




